Popularity Adjusted Block Models are Generalized Random Dot Product Graphs

### 2022-03-30 fls-lightning-talk/slides.Rmd
updated notes/script

**Theorem** (KTT): $A \sim \PABM(\{\lambda^{(kl)}\}_K)$ is equivalent to 
$A \sim \GRDPG_{p, q}(X U)$ with

@@

**Theorem** (KTT): 
Let $\hat{B}$ with entries $\hat{B}_{ij}$ be the affinity matrix from OSC. 
Then $\forall$ pairs $(i, j)$ belonging to different communities 
and sparsity factor satisfying $n \rho_n = \omega\big((\log n)^{4c}\big)$,

$\max_{i, j} \hat{B}_{ij} = 
O_P \Big( \frac{(\log n)^c}{\sqrt{n \rho_n}} \Big)$ 
as $n \to \infty$.

>>>>

**Theorem** (KTT): $A \sim \PABM(\{\lambda_{ik}\}_K)$ is equivalent to 
$A \sim \GRDPG_{p, q}(X U)$ with

@@

**Theorem** (KTT): 
Let $\hat{B}$ with entries $\hat{B}_{ij}$ be the affinity matrix from OSC. 
Then $\forall$ pairs $(i, j)$ belonging to different communities 
and sparsity factor satisfying $n \rho_n = \omega\big((\log n)^{4c}\big)$,  
$\max_{i, j} \hat{B}_{ij} = 
O_P \Big( \frac{(\log n)^c}{\sqrt{n \rho_n}} \Big)$ 
as $n \to \infty$.

### 2022-03-30 fls-lightning-talk/slides.tex
updated notes/script

\begin{frame}{Connecting the PABM to the GRDPG}
\protect\hypertarget{connecting-the-pabm-to-the-grdpg}{}
\textbf{Theorem} (KTT): \(A \sim \text{PABM}(\{\lambda^{(kl)}\}_K)\) is
equivalent to \(A \sim \text{GRDPG}_{p, q}(X U)\) with

@@

\textbf{Theorem} (KTT): Let \(\hat{B}\) with entries \(\hat{B}_{ij}\) be
the affinity matrix from OSC. Then \(\forall\) pairs \((i, j)\)
belonging to different communities and sparsity factor satisfying
\(n \rho_n = \omega\big((\log n)^{4c}\big)\),

\(\max_{i, j} \hat{B}_{ij} = O_P \Big( \frac{(\log n)^c}{\sqrt{n \rho_n}} \Big)\)
as \(n \to \infty\).
\end{frame}

@@

\begin{itemize}
\tightlist
\item
  Modularity Maximization (Sengupta and Chen) using the Louvain
  algorithm;
\item
  Orthogonal Spectral Clustering (KTT);
\item
  Sparse Subspace Clustering on the columns of \(A\) (Noorozi, Rimal,
  Pensky);
\item
  Sparse Subspace Clustering on the ASE (KTT).
\end{itemize}

>>>>

\begin{frame}{Connecting the PABM to the GRDPG}
\protect\hypertarget{connecting-the-pabm-to-the-grdpg}{}
\textbf{Theorem} (KTT): \(A \sim \text{PABM}(\{\lambda_{ik}\}_K)\) is
equivalent to \(A \sim \text{GRDPG}_{p, q}(X U)\) with

@@

\textbf{Theorem} (KTT): Let \(\hat{B}\) with entries \(\hat{B}_{ij}\) be
the affinity matrix from OSC. Then \(\forall\) pairs \((i, j)\)
belonging to different communities and sparsity factor satisfying
\(n \rho_n = \omega\big((\log n)^{4c}\big)\),\\
\(\max_{i, j} \hat{B}_{ij} = O_P \Big( \frac{(\log n)^c}{\sqrt{n \rho_n}} \Big)\)
as \(n \to \infty\).
\end{frame}

@@

\begin{itemize}
\tightlist
\item
  Modularity Maximization (Sengupta and Chen) using the Louvain
  algorithm;
\item
  Orthogonal Spectral Clustering (KTT);
\item
  Sparse Subspace Clustering on the columns of \(A\)\\
  (Noorozi, Rimal, Pensky);
\item
  Sparse Subspace Clustering on the ASE (KTT).
\end{itemize}
